Flatiron cleaning

### 2021-12-16 Rmd/rdi analysis.Rmd
Update imputation

```{r consort}
library(ggconsort)
# flatiron_rec <- Frontline_adjusted %>% 
#   filter(is.na(flatiron_rules))
# study_criteria <- flatiron_rec %>% 
#   filter(!is.na(histology))
# study_criteria <- study_criteria %>%
#   filter(!is.na(surgerydate))
# study_criteria <- study_criteria %>%
#   filter(had_carbo_pacli == "Yes")
# study_criteria <- study_criteria %>% 
#   filter(treatment_sequence == "neo + surg + adj" |
#            treatment_sequence == "surg + adj")
# study_criteria <- study_criteria %>%
#   filter(is.na(line_keep))
#

study_cohorts <- 
  Frontline_adjusted %>%
  cohort_start("Assessed for eligibility") %>%
  # Define cohorts using named expressions
  # Notice that you can use previously defined cohorts in subsequent steps
  cohort_define(
  flatiron_rec = .full %>% filter(is.na(flatiron_rules)),

@@

  ) %>%
  consort_box_add(
    "study_criteria", 5, 40, cohort_count_adorn(study_cohorts, study_criteria)
  ) %>%
  consort_box_add(
    "missing_data", 5, 35, cohort_count_adorn(study_cohorts, missing_data)
  ) %>%
  consort_box_add(
    "standard_care", 5, 30, cohort_count_adorn(study_cohorts, standard_care)
  ) %>%
  consort_box_add(
    "Frontline", 5, 25, cohort_count_adorn(study_cohorts, Frontline)
  ) %>%
  consort_box_add(
    "Frontline1", 0, 20, cohort_count_adorn(study_cohorts, Frontline1)
  ) %>%

  consort_arrow_add(
    end = "flatiron_rec", end_side = "left", start_x = 0, start_y = 45
  ) %>%
  consort_arrow_add(
    end = "study_criteria", end_side = "left", start_x = 0, start_y = 40
  ) %>%
  consort_arrow_add(
    end = "missing_data", end_side = "left", start_x = 0, start_y = 35
  ) %>%
  consort_arrow_add(
    end = "standard_care", end_side = "left", start_x = 0, start_y = 30
  ) %>%
  consort_arrow_add(
    end = "Frontline", end_side = "left", start_x = 0, start_y = 25
  ) %>%
  consort_arrow_add(
    end = "Frontline1", end_side = "top", start_x = 0, start_y = 50
  )

study_consort %>%
  ggplot() + 
  geom_consort() +
  theme_consort(margin_h = 8, margin_v = 1)
```

@@

           "histology", imp_histology, "stagecat", imp_stagecat,

@@

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= imp_histology))+
  geom_bar()+
  theme_minimal(base_size = 14)+
  labs(title = "Histology")+
  coord_flip()

@@

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= raceeth, fill = imp_histology))+
  geom_bar(position = "fill")+
  theme_minimal(base_size = 14)+
  labs(title = "Histology")+
  coord_flip()

@@

<span style="color:green">**RDI summary table**</span>

@@

reset_gtsummary_theme()
set_gtsummary_theme(my_theme)
trial %>%
  select(age, grade, trt) %>%
  tbl_summary(by = trt) %>%
  add_stat_label() %>%
  add_p() %>%
  as_gt() 
```

```{r Table summary Platin}
# Treatment & demo
tbl1 <- Frontline %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("RDI (continous)" = RDI_carbo_neo, "RDI (categorical)" = RDI_carbo_neo_grp, therapy)) %>%
  tbl_summary(by = therapy) %>% 
  bold_labels()

tbl2 <- Frontline %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("RDI (continous)" = RDI_carbo_adj, "RDI (categorical)" = RDI_carbo_adj_grp, therapy)) %>%
  tbl_summary(by = therapy) %>%
  bold_labels()

tbl3 <- Frontline %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("RDI (continous)" = RDI_pacli_neo, "RDI (categorical)" = RDI_pacli_neo_grp, therapy)) %>%
  tbl_summary(by = therapy
              ) %>%
  bold_labels()

tbl4 <- Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("RDI (continous)" = RDI_pacli_adj, "RDI (categorical)" = RDI_pacli_adj_grp, therapy)) %>%
  tbl_summary(by = therapy
              ) %>%
  bold_labels()
tbl5 <- Frontline %>% filter(dose_dense == 3) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("RDI (continous)" = RDI_pacli_neo, "RDI (categorical)" = RDI_pacli_neo_grp, therapy)) %>%
  tbl_summary(by = therapy,
              type = list(`RDI (continous)` ~ "continuous")) %>%
  bold_labels()
tbl6 <- Frontline %>% filter(dose_dense == 3) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("RDI (continous)" = RDI_pacli_adj, "RDI (categorical)" = RDI_pacli_adj_grp, therapy)) %>%
  tbl_summary(by = therapy,
              type = list(`RDI (continous)` ~ "continuous")) %>%
  bold_labels()

@@

<span style="color:green">**Table 4 Summary RDI data by race and bmi**</span>  
Removing the overall on the right side? Or do you want the tables separated?
Platin  
```{r Table4 summary Platin}
tbl1 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "RDI" = RDI_carbo_neo, "RDI cat" = RDI_carbo_neo_grp)) %>%
  tbl_summary(by = raceeth) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05)
tbl2 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat, "RDI" = RDI_carbo_neo, "RDI cat" = RDI_carbo_neo_grp)) %>%
  tbl_summary(by = bmi_cat) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05)

@@

<span style="color:green">**Table 6 HR**</span>

@@

## Multivariable
### RDI group
`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~RDI_grp + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking` 
```{r Table 5 HR adjusted rdi group}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("carboplatin Neo/Upfront Chemo", 
                           "carboplatin Adj/Upfront Chemo",
                           "carboplatin Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()

@@

tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_pacli_neo_grp + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vitalstatus) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("paclitaxel Neo/Upfront Chemo", 
                           "paclitaxel Adj/Upfront Chemo",
                           "paclitaxel Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
<!-- In multivariable analysis, categorical RDI for carboplatin or paclitaxel is not a factor associated with survival. -->

@@

### Continous
`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ mean_RDI_per_drug + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking` 
```{r rdi continous}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_carbo_neo + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vitalstatus) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("carboplatin Neo/Upfront Chemo", 
                           "carboplatin Adj/Upfront Chemo",
                           "carboplatin Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()

@@

tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_pacli_neo + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vitalstatus) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("paclitaxel Neo/Upfront Chemo", 
                           "paclitaxel Adj/Upfront Chemo",
                           "paclitaxel Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
<!-- In multivariable analysis, a higher RDI for carboplatin shows a worse survival (p<0.001) in an Adjuvant / Upfront Chemo setting as seen in the univariable analysis.   -->
<!-- RDI for paclitaxel is not a factor associated with survival. -->

@@

## Adjusted by other drug
### RDI group
`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking` 
```{r Table 5 HR adjusted rdi group adjusted by other drug}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl2, tbl3),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
<!-- When adjusting by each drugs, we observe a 61% increased risk of death for a underdosing of carboplatin in the Neoadjuvant / Upfront Chemo setting (p=0.059) and a 32% increased risk of death for a underdosing of paclitaxel in the Adjuvant / Upfront Surgery setting (p=0.059). -->

@@

### Continous
`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat` 
```{r rdi continous adjusted by other drug}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vitalstatus) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl2, tbl3),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
<!-- Continuous RDI for carboplatin or paclitaxel are not factors associated with survival. -->

>>>>

```{r consort}
library(ggconsort)
study_cohorts <- 
  Frontline_adjusted %>%
  cohort_start("Assessed for eligibility") %>%
  # Define cohorts using named expressions
  # Notice that you can use previously defined cohorts in subsequent steps
  cohort_define(
  flatiron_rec = .full %>% filter(is.na(flatiron_rules)),

@@

  ) %>%
  consort_box_add(
    "study_criteria", 5, 35, cohort_count_adorn(study_cohorts, study_criteria)
  ) %>%
  consort_box_add(
    "missing_data", 5, 30, cohort_count_adorn(study_cohorts, missing_data)
  ) %>%
  consort_box_add(
    "standard_care", 5, 25, cohort_count_adorn(study_cohorts, standard_care)
  ) %>%
  consort_box_add(
    "Frontline", 5, 20, cohort_count_adorn(study_cohorts, Frontline)
  ) %>%
  consort_box_add(
    "Frontline1", 0, 15, cohort_count_adorn(study_cohorts, Frontline1)
  ) %>%

  consort_arrow_add(
    end = "flatiron_rec", end_side = "left", start_x = 0, start_y = 45
  ) %>%
  consort_arrow_add(
    end = "study_criteria", end_side = "left", start_x = 0, start_y = 35
  ) %>%
  consort_arrow_add(
    end = "missing_data", end_side = "left", start_x = 0, start_y = 30
  ) %>%
  consort_arrow_add(
    end = "standard_care", end_side = "left", start_x = 0, start_y = 25
  ) %>%
  consort_arrow_add(
    end = "Frontline", end_side = "left", start_x = 0, start_y = 20
  ) %>%
  consort_arrow_add(
    end = "Frontline1", end_side = "top", start_x = 0, start_y = 50
  )

study_consort %>%
  ggplot() + 
  geom_consort() +
  theme_consort(margin_h = 18, margin_v = 1)
```

@@

           "histology", "stagecat", imp_stagecat,

@@

@@

@@

<span style="color:green">**Table 6: RDI summary table**</span>

@@

reset_gtsummary_theme()
set_gtsummary_theme(my_theme)

# trial %>%
#   select(age, grade, trt) %>%
#   tbl_summary(by = trt) %>%
#   add_stat_label() %>%
#   add_p() %>%
#   as_gt() 
```

```{r Table summary Platin}
# Treatment & demo
tbl1 <- Frontline %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("RDI (continous)" = RDI_carbo_neo, "RDI (categorical)" = RDI_carbo_neo_grp, therapy)) %>%
  tbl_summary(by = therapy) %>% 
  bold_labels() %>% add_n() %>% add_overall()

tbl2 <- Frontline %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("RDI (continous)" = RDI_carbo_adj, "RDI (categorical)" = RDI_carbo_adj_grp, therapy)) %>%
  tbl_summary(by = therapy) %>%
  bold_labels() %>% add_n() %>% add_overall()

tbl3 <- Frontline %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("RDI (continous)" = RDI_pacli_neo, "RDI (categorical)" = RDI_pacli_neo_grp, therapy)) %>%
  tbl_summary(by = therapy
              ) %>%
  bold_labels() %>% add_n() %>% add_overall()

tbl4 <- Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("RDI (continous)" = RDI_pacli_adj, "RDI (categorical)" = RDI_pacli_adj_grp, therapy)) %>%
  tbl_summary(by = therapy
              ) %>%
  bold_labels() %>% add_n() %>% add_overall()
tbl5 <- Frontline %>% filter(dose_dense == 3) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("RDI (continous)" = RDI_pacli_neo, "RDI (categorical)" = RDI_pacli_neo_grp, therapy)) %>%
  tbl_summary(by = therapy,
              type = list(`RDI (continous)` ~ "continuous")) %>%
  bold_labels() %>% add_n() %>% add_overall()
tbl6 <- Frontline %>% filter(dose_dense == 3) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("RDI (continous)" = RDI_pacli_adj, "RDI (categorical)" = RDI_pacli_adj_grp, therapy)) %>%
  tbl_summary(by = therapy,
              type = list(`RDI (continous)` ~ "continuous")) %>%
  bold_labels() %>% add_n() %>% add_overall()

@@

<span style="color:green">**Table 7: Summary RDI data by race and bmi**</span>  
Removing the overall on the right side? Or do you want the tables separated?
Platin  
```{r Table4 summary Platin}
tbl1 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "RDI" = RDI_carbo_neo, "RDI cat" = RDI_carbo_neo_grp)) %>%
  tbl_summary(by = raceeth) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05)
tbl2 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat, "RDI" = RDI_carbo_neo, "RDI cat" = RDI_carbo_neo_grp)) %>%
  tbl_summary(by = bmi_cat) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05)

@@

<span style="color:green">**Table 8 HR Univariable**</span>

@@

## Multivariable
### RDI group
<span style="color:green">**Table 9 HR Multivariable**</span>

`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~RDI_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking` 
```{r Table 5 HR adjusted rdi group}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("carboplatin Neo/Upfront Chemo", 
                           "carboplatin Adj/Upfront Chemo",
                           "carboplatin Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()

@@

tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_pacli_neo_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vitalstatus) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("paclitaxel Neo/Upfront Chemo", 
                           "paclitaxel Adj/Upfront Chemo",
                           "paclitaxel Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
<!-- In multivariable analysis, categorical RDI for carboplatin or paclitaxel is not a factor associated with survival. -->

@@

### Continous
<span style="color:green">**Table 10 HR Multivariable**</span>

`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ mean_RDI_per_drug + raceeth + ageatdx + imp_stagecat + histology + imp_debulking` 
```{r rdi continous}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_carbo_neo + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vitalstatus) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("carboplatin Neo/Upfront Chemo", 
                           "carboplatin Adj/Upfront Chemo",
                           "carboplatin Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()

@@

tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_pacli_neo + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vitalstatus) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("paclitaxel Neo/Upfront Chemo", 
                           "paclitaxel Adj/Upfront Chemo",
                           "paclitaxel Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
<!-- In multivariable analysis, a higher RDI for carboplatin shows a worse survival (p<0.001) in an Adjuvant / Upfront Chemo setting as seen in the univariable analysis.   -->
<!-- RDI for paclitaxel is not a factor associated with survival. -->

@@

## Adjusted by other drug
### RDI group
<span style="color:green">**Table 11 HR Multivariable**</span>

`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking` 
```{r Table 5 HR adjusted rdi group adjusted by other drug}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl2, tbl3),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
<!-- When adjusting by each drugs, we observe a 61% increased risk of death for a underdosing of carboplatin in the Neoadjuvant / Upfront Chemo setting (p=0.059) and a 32% increased risk of death for a underdosing of paclitaxel in the Adjuvant / Upfront Surgery setting (p=0.059). -->

@@

### Continous
<span style="color:green">**Table 12 HR Multivariable**</span>

`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat` 
```{r rdi continous adjusted by other drug}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vitalstatus) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl2, tbl3),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
<!-- Continuous RDI for carboplatin or paclitaxel are not factors associated with survival. -->
